Title

### 2014-01-15 paper/parts/methods.tex
Fixed some broken pointers to tables / sections. Modified the header to include section numbers.
Fixed minor typo.

\subsection{Activity-Based Communities and Transfer Entropy}

\label{method-activity}

@@

In estimating the transfer entropy from finite data, we will assume that the process $(X_{t}, Y_{t})$ is jointly stationary, which gives us that
\begin{align}
	p(x_{t} | x_{t-k}^{t-1}) = p(x_{k+1} | x_{1}^{k})
\end{align}
and
\begin{align}
	p(x_{t} | x_{t-k}^{t-1}, y_{t-k}^{t-1}) = p(x_{k+1} | x_{1}^{k}, y_{1}^{k})
\end{align}
for all $t$. That is, the predictive distribution only depends on the past, not on when the past is observed\footnote{We really only need \emph{conditional} stationarity~\cite{caires2003nonparametric}, but stationarity implies conditional stationarity}. Given this assumption, we compute estimators for $p(x_{k+1} | x_{1}^{k})$ and $p(x_{k+1} | x_{1}^{k}, y_{1}^{k})$ by `counting': for each possible past $(x_{1}^{k}, y_{1}^{k})$, we count the number of times a future of type $x_{k+1}$ occurs, and normalize. Call these estimators $\hat{p}(x_{k+1} | x_{1}^{k})$ and $\hat{p}(x_{k+1} | x_{1}^{k}, y_{1}^{k})$. Then the plug-in estimator for the transfer entropy is
\begin{align}
	\widehat{\text{TE}}_{Y \to X}^{(k)} &= \hat{H}\left[X_{t} | X_{t-k}^{t-1}\right] - \hat{H}\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]
\end{align}
where we use the plug-in estimators $\hat{H}\left[X_{t} | X_{t-k}^{t-1}\right]$ and $\hat{H}\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$ for the entropies. It is well known that the plug-in estimator for entropy is biased~\cite{paninski2003estimation}. To account for this bias, we use the Miller-Madow adjustment to the plug-in estimator~\cite{miller1955note}.

@@

\section{Interaction-Based Communities and Mention / Retweet Weighting}

\label{method-interaction}

@@

\section{Topic-based Communities and Hashtag Weighting}

\label{method-topic}

>>>>

\subsection{Activity-Based Communities and Transfer Entropy}
\label{sec:method-activity}

@@

In estimating the transfer entropy from finite data, we will assume that the process $(X_{t}, Y_{t})$ is jointly stationary, which gives us that
\begin{align}
	p(x_{t} | x_{t-k}^{t-1}) = p(x_{k+1} | x_{1}^{k})
\end{align}
and
\begin{align}
	p(x_{t} | x_{t-k}^{t-1}, y_{t-k}^{t-1}) = p(x_{k+1} | x_{1}^{k}, y_{1}^{k})
\end{align}
for all $t$. That is, the predictive distribution only depends on the past, not on when the past is observed\footnote{We really only need \emph{conditional} stationarity~\cite{caires2003nonparametric}, but stationarity implies conditional stationarity.}. Given this assumption, we compute estimators for $p(x_{k+1} | x_{1}^{k})$ and $p(x_{k+1} | x_{1}^{k}, y_{1}^{k})$ by `counting': for each possible past $(x_{1}^{k}, y_{1}^{k})$, we count the number of times a future of type $x_{k+1}$ occurs, and normalize. Call these estimators $\hat{p}(x_{k+1} | x_{1}^{k})$ and $\hat{p}(x_{k+1} | x_{1}^{k}, y_{1}^{k})$. Then the plug-in estimator for the transfer entropy is
\begin{align}
	\widehat{\text{TE}}_{Y \to X}^{(k)} &= \hat{H}\left[X_{t} | X_{t-k}^{t-1}\right] - \hat{H}\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]
\end{align}
where we use the plug-in estimators $\hat{H}\left[X_{t} | X_{t-k}^{t-1}\right]$ and $\hat{H}\left[X_{t} | X_{t-k}^{t-1}, Y_{t-k}^{t-1}\right]$ for the entropies. It is well known that the plug-in estimator for entropy is biased~\cite{paninski2003estimation}. To account for this bias, we use the Miller-Madow adjustment to the plug-in estimator~\cite{miller1955note}.

@@

\subsection{Interaction-Based Communities and Mention / Retweet Weighting}
\label{sec:method-interaction}

@@

\subsection{Topic-based Communities and Hashtag Weighting}
\label{sec:method-topic}
